A Method for Regularisation of Evolutionary Polynomial Regressions using Support Vector Machines

### 2013-11-20 texts/submission_02-asc/paper_spfga-review.tex
New Abstract

%
%	ACRONYMS
%
\usepackage{acronym}
%
\acrodef{GA}{Genetic algorithms}
\acrodef{rmse}[error]{root-mean-square error}
\acrodef{GAPoly}[\textsc{GAPoly}]{Genetic Algorithms for Polynomials}
\acrodef{EPR}{Evolutionary Polynomial Regression}
%

@@

\address[ue]{Dept. Informática, Universidade de Évora, Rua Romão Ramalho 58, 7000-671 Évora}
\address[fcul]{Dept. Informática, Faculdade de Ciências da Universidade de Lisboa, Campo Grande 1749-016 Lisboa}
\address[labmag]{Laboratory of Agent Modelling (LabMAg)}
%
%\date{[{\sc draft} \today]}
%
\begin{abstract}
Many applications require models that have no acceptable linear approximation and the simpler nonlinear models are defined by polynomials. The use of genetic algorithms to find polynomial models, \ac{EPR}, provides an automatic method to build such model from data but still poses challenges due to the complexity of the search and different definitions of optimal solution.

This paper describes a two-step method that uses genetic algorithms and linear regression to find empirical polynomial regressions. Experiments on common datasets show that, discounting the training computational effort, this method is quite competitive.
\end{abstract}
%
\begin{keyword}
evolutionary polynomial regression \sep regularization \sep feature extraction \sep dimensionality reduction 
\end{keyword}
\end{frontmatter}
%
%	Line numbers for revision
%
%
\linenumbers
%
\section{Introduction}

@@

Polynomials, one of the most studied subjects in mathematics, generalize li\-ne\-ar functions and define, perhaps, the simplest and most used nonlinear models. Applications include colorimetric calibration \citep{mendes2005adaptive}, explicit formul\ae\ for turbulent pipe flows \citep{davidson1999method}, computational linguistics \citep{sanchez2009obtaining} and more recently, analytical techniques for cultural heritage materials \citep{csefalvayova2010use}, liquid epoxy molding process \citep{chan2011modeling}, B-spline surface reconstruction \citep{galvez2012iterative}, product design \citep{chan2012development} or forecasting cyanotoxins presence in water reservoirs \citep{garcia2013hybrid}. These examples not only illustrate the wide spectrum of applications but, additionally, work in each one uses, at some point, a genetic algorithm.

\ac{GA} where, arguably, one of the hottest topics of research in the recent decades and with good reason since they outline an optimization scheme easy to conceptualize and with very broad application. If a nonlinear (or otherwise) model requires parameterization \acp{GA} provide a simple and often effective approach to search for locally optimal parameters. Research related to genetic algorithms abound and spans from the 1950s seminal work of Nils Aall Barricelli \citep{barricelli1962numerical} in the Institute for Advanced Study of Princeton to today's principal area of study for thousands of researchers, covered in hundreds of conferences, workshops and other meetings. Perhaps the key impulse to \acp{GA} come from John Holland's work and his book ``Adaptation in Natural and Artificial Systems'' \citep{holland1975adaptation}.

>>>>

%
%	ACRONYMS
%
\usepackage{acronym}
%
\acrodef{GA}{Genetic algorithms}
\acrodef{rmse}[error]{root-mean-square error}
\acrodef{GAPoly}[\textsc{GAPoly}]{Genetic Algorithms for Polynomials}
\acrodef{EPR}{Evolutionary Polynomial Regression}
\acrodef{EPRR}[EPR$^2$]{Evolutionary Polynomial Regression with Regularisation}
%

@@

\address[ue]{Dept. Informática, Universidade de Évora, Rua Romão Ramalho 58, 7000-671 Évora}
\address[fcul]{Dept. Informática, Faculdade de Ciências da Universidade de Lisboa, Campo Grande 1749-016 Lisboa}
\address[labmag]{Laboratory of Agent Modelling (LabMAg)}
%
%\date{[{\sc draft} \today]}
%
\begin{abstract}
While many applications require models that have no acceptable linear approximation the simpler nonlinear models are defined by polynomials. The use of genetic algorithms to find polynomial models, \ac{EPR}, provides an automatic method to build such models from data but still poses challenges due to the complexity of the search and different definitions of optimal solution.

This paper describes \ac{EPRR}, an algorithm that extends the general \ac{EPR} method with regularisation and a set of experiences to compare both flavours of \ac{EPR} and other usual regression methods including Random Forests, Linear Regression and Support Vector Machines on common datasets. The empiric conclusion of those experiments is that \ac{EPRR} achieves better fitting errors and that, with respect to the plain \ac{EPR}, computation time is shorter.
\end{abstract}
%
\begin{keyword}
evolutionary polynomial regression \sep regularisation \sep feature extraction \sep dimensionality reduction 
\end{keyword}
\end{frontmatter}
%
%	Line numbers for revision
%
%
\linenumbers
%
\section{Introduction}

@@

Polynomials, one of the most studied subjects in mathematics, generalise li\-ne\-ar functions and define, perhaps, the simplest and most used nonlinear models. Applications include colorimetric calibration \citep{mendes2005adaptive}, explicit formul\ae\ for turbulent pipe flows \citep{davidson1999method}, computational linguistics \citep{sanchez2009obtaining} and more recently, analytical techniques for cultural heritage materials \citep{csefalvayova2010use}, liquid epoxy moulding process \citep{chan2011modeling}, B-spline surface reconstruction \citep{galvez2012iterative}, product design \citep{chan2012development} or forecasting cyanotoxins presence in water reservoirs \citep{garcia2013hybrid}. These examples not only illustrate the wide spectrum of applications but, additionally, work in each one uses, at some point, a genetic algorithm.

\ac{GA} where, arguably, one of the hottest topics of research in the recent decades and with good reason since they outline an optimisation scheme easy to conceptualise and with very broad application. If a nonlinear (or otherwise) model requires parameterization \acp{GA} provide a simple and often effective approach to search for locally optimal parameters. Research related to genetic algorithms abound and spans from the 1950s seminal work of Nils Aall Barricelli \citep{barricelli1962numerical} in the Institute for Advanced Study of Princeton to today's principal area of study for thousands of researchers, covered in hundreds of conferences, workshops and other meetings. Perhaps the key impulse to \acp{GA} come from John Holland's work and his book ``Adaptation in Natural and Artificial Systems'' \citep{holland1975adaptation}.
